PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-06 paper/sec-results.tex
z-pt part

\paragraph{Z-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. So far, this measurement has not been
included in any PDF determination. Because it has sub-percent experimental uncertainties,
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with the LO and NLO EW corrections,
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 100 (165) parton luminosities,
see appendix~\ref{app:lumis} for details.

@@

Finally, we implement the kinematic cuts specified in the corresponding
experimental analyses. In the case of high-mass Drell--Yan lepton pair
production at \SI{7}{\tera\electronvolt} measured by ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
$|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
momentum and the pseudorapidity of each lepton and for the invariant mass of the
lepton pair, respectively. In the case of double-differential Drell--Yan
lepton-pair production
at \SI{7}{\tera\electronvolt} measured by CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
for the transverse momentum and the pseudorapidity of each lepton, and for the
pseudorapidity and the invariant mass of the lepton pair. In the case of Z-boson
production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS, we
require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
$M_\mathrm{Z}-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_\mathrm{Z}+\SI{20}{\giga\electronvolt}$,
$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
pseudorapidity and transverse momentum of the lepton pair.

>>>>

\paragraph{Z-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
included in any PDF determination, its expected impact on parton densities has been studied in 
ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with the LO and NLO EW corrections,
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alpha^4)$, and with the NLO
QCD-EW mixed-coupling correction, $\mathcal{O}(\alphas\alpha^3)$. EW corrections for
this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 100 (165) parton luminosities,
see appendix~\ref{app:lumis} for details.

@@

Finally, we implement the kinematic cuts specified in the corresponding
experimental analyses. In the case of high-mass Drell--Yan lepton pair
production at \SI{7}{\tera\electronvolt} measured by ATLAS, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
$|\eta_\ell|<2.5$ and $\SI{116}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the transverse
momentum and the pseudorapidity of each lepton and for the invariant mass of the
lepton pair, respectively. In the case of double-differential Drell--Yan
lepton-pair production
at \SI{7}{\tera\electronvolt} measured by CMS, we require $p_\mathrm{T}^{\ell_1}>\SI{14}{\giga\electronvolt}$, $p_\mathrm{T}^{\ell_2}>\SI{9}{\giga\electronvolt}$,
$|\eta_\ell|<2.4$, $|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$
for the transverse momentum and the pseudorapidity of each lepton, and for the
pseudorapidity and the invariant mass of the lepton pair. In the case of Z-boson
production with non-zero transverse momentum at \SI{13}{\tera\electronvolt} measured by CMS,
require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
$M_\mathrm{Z}-\SI{15}{\giga\electronvolt}<M_{\ell\bar\ell}<M_\mathrm{Z}+\SI{20}{\giga\electronvolt}$,
$|\eta_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
is necessary as we stick to a fixed-order computation, without including resummation effects.
